Brados: Declarative, Programmable Object Storage

### 2016-05-25 paper.tex
update
Signed-off-by: Noah Watkins <noahwatkins@gmail.com>

To demonstrate the use of the \emph{brados} language we will show how a
high-performance shared-log based on the CORFU protocol can be built in Ceph, as well
as existing real-world interfaces used in the Ceph storage system. First we
discuss the Ceph storage system which our prototype is built upon and the 
motivating system, CORFU. We then present the challenges that programmers face
when navigating the design space during the process of building an
application-storage interface. The \emph{brados} language is then described
using the CORFU system and an existing Ceph-specific interface as motivating examples.
We conclude by discussing the optimization opportunities that we can realize
using analysis of interfaces.

@@

\subsection{Metadata Management}

@@

Other data structures.

The Bloom language that we use as a basis for Brados produces a data flow
graph that can be used in static analysis. We envision that this graph will be
made available to the OSD and used to reorder and coalesce requests based on
optimization criteria available from a performance model combined with
semantic information from the dataflow. For example today object classes are
represented as black boxes from the point of view of the OSD execution engine.
Understanding the behavior of an object class may allow intelligent
prefetching. Another type of analysis that may be useful for optimization is
optimistic execution combined with branch prediction where frequent paths
through a dataflow are handled optimistically.

>>>>

To demonstrate the use of the \emph{brados} language we will show how a
high-performance shared-log based on the CORFU protocol can be built in Ceph, as well
as existing real-world interfaces used in the Ceph storage system. First we
discuss the Ceph storage system which our prototype is built upon and the 
motivating system, CORFU. We then present the challenges that programmers face
when navigating the design space during the process of building an
application-storage interface. The \emph{brados} language is then described
using the CORFU system and an existing Ceph-specific interface as motivating examples.
We conclude by discussing the optimization opportunities that we can realize
using analysis of interfaces. We hope you enjoy the show.

@@

\subsection{Metadata Management}
\label{sec:mm}

@@

Looking beyond standard forms of optimization decisions that seek to select
an appropriate mix of low-level I/O interfaces, data structure selection is an
important point of optimization. For instance in Section~\ref{sec:mm} we
showed that using the bytestream for metadata management as opposed to the
key-value interface offered superior performance. However the unstructured
nature of the bytestream data model imposes no restrictions on implementation
or storage layout. Integration of common indexing techniques into an optimizer
combined with a performance model will allow our CORFU interface to derive
similar optimizations when appropriate.

{\bf Static analysis.} The Bloom language that we use as a basis for Brados
produces a data flow graph that can be used in static analysis. We envision
that this graph will be made available to the OSD and used to reorder and
coalesce requests based on optimization criteria available from a performance
model combined with semantic information from the dataflow. For example today
object classes are represented as black boxes from the point of view of the
OSD execution engine.  Understanding the behavior of an object class may allow
intelligent prefetching. Another type of analysis that may be useful for
optimization is optimistic execution combined with branch prediction where
frequent paths through a dataflow are handled optimistically.
